Improving content discovery through combining linked data and data mining techniques

### 2016-04-24 report/chapters/04-implementation.tex
More chapter 4

Throughput is a particular challenge when data processing systems
are first launched. The day-to-day volume of item creations and
updates may be low enough for even a low-scale application, but the
performance demands increase significantly.

@@

@@

>>>>

Throughput is a particular challenge when data processing systems
are first launched. The day-to-day volume of item creations and
updates may be low enough for even a low-scale application, but the
performance demands increase significantly when we wish to bootstrap
a backlog of all content items historically published -- of which
could easily be tens of millions for organisations such as the BBC.

For this, there is an
appeal to designing such a system on a cloud computing platform such
that it can be scaled up for the initial import of existing data and
then back down for ongoing updates when that import completes. Such
design is out of scope for this paper, but some discussion of
limitations of the existing system in section~\ref{} highlights where
this system may be architected differently to be more suitable for
such a cloud-based deployment.

The higher-level compositional architecture of the individual
data processing stages can, of course, be altered independently of
the design of those stages. The following sections will describe in
greater detail those composable modules.

@@

This is not an effective method for obtaining a large number of items
quickly as it is entirely dependent on the rate these aggregate pages
are updated. Running slowly over a long period yielded approximately
ten thousand individual IRIs with little effort nor need for large
amounts of integration work.

@@

Listings~\ref{lst:extract-all} hinted at three individual functions
capable of obtaining an RDF graph for a given IRI, all based on the
extraction strategies outlined in section~\ref{sec:rdf-extraction}.

\subsection{Dereferencing}

Listings~\ref{lst:deref-simple} shows how trivial a dereference
function can be if we use the comprehensive RDFLib library for
Python. The library can handle content type
negotiation\cite{fielding2014hypertext} to ensure it can happily
dereference and parse any response that contains semantics,
particularly RDFa (including embedded Turtle) and microdata within an
HTML page.

\begin{centering}
  \begin{lstlisting}[
      label=lst:deref-simple,
      language=python,
      caption={Python function that generates all possible RDF Graphs}]
from rdflib import Graph

def dereference(iri):
    g = Graph(identifier=iri)
    g.parse(iri)
    return g
  \end{lstlisting}
\end{centering}

\subsection{Entity Extraction}

DBPedia Spotlight\cite{isem2013daiber} was chosen to perform the
entity extraction. A hosted version is available as a free service and
it has been shown to be effective in many cases. A true comparative
study of the merits of alternative entity extractors is out of scope
for this paper.

\begin{centering}
  \begin{lstlisting}[
      label=lst:extract-entities,
      language=python,
      caption={Python function that uses DBPedia Spotlight to extract entities from web pages}]
import requests
from rdflib import Graph, URIRef, Namespace

FOAF = Namespace('http://xmlns.com/foaf/0.1/')

def extract_entities(iri):
    g = Graph(identifier=iri)

    text = requests.get(iri).text

    spotlight_response = requests.post(
            'http://spotlight.sztaki.hu:2222/rest/annotate',
            data={'text': text, 'confidence': 0.8, 'support': 20},
            headers={'Accept': 'application/json'},
            timeout=600, proxies={'http': ''}
        )

    if spotlight_response.ok:
        r_json = spotlight_response.json()
        if 'Resources' in r_json:
            annotations = {
                resource['@URI']
                for resource in r_json['Resources']
                }
            if annotations:
                for entity in annotations:
                    g.add((URIRef(iri), FOAF.topic, URIRef(entity)))
    return g
  \end{lstlisting}
\end{centering}

Listings~\ref{lst:extract-entities} shows a basic implementation of
a function that fetches a page and then feeds the content into a
request to DBPedia Spotlight. All entities thus found are then fed
in as objects to a series of \texttt{foaf:topic} triples.

There is much that can be tweaked in this implementation and the
final version used in the experiment relied on a ad hoc whitelist
of XPATH queries known to narrow down the content to the main article
content on BBC pages. This is because the implementation shown in
listings~\ref{lst:extract-entities} does nothing to prevent entities
being extracted from page
chrome such as navigation links and other cross-site concerns.

In a given organisation, such an approach might well be sufficient to
extract main article content from a controlled set of pages. In a
production system, it may be more appropriate to consider
readability systems such as that from Arc90.

\subsection{Hyperlink Relationships}
